---
title: "Example Covid Report"
author: "INFO-201: Class Demo"
date: "2/7/2022"
output: html_document
---

```{r setup, include=FALSE}
source("C:/Users/jbkka/Documents/info201/assignments/X10/rmd-practice-admin-jbkauff/source/analysis.R")
knitr::opts_chunk$set(echo = TRUE)
```

## Covid Report
Within the analysis.R file, I examined a data set pertaining to the NYT COVID-19 data on a national scale. Within this data set, I used the 'get_total_cases()' function and  found that the total number of US cases is 97,654,808. I used the 'get_total_deaths()' function to find that the total number of US deaths is 1,069,792.
 
(**Note**: Why are there no commas in the *total number of US deaths* ? Can you change `analysis.R` file so that the number is commented with commas?)
There is no commas in the *total number of US deaths* because in the original function, it did not utilize the 'prettyNum()' function to create commas that separate the integers. The change is reflected on the 'analysis.R' file.

I also want to show the chart:
``` {r echo=FALSE}
cases_plot
```


